---
title: "my-model-description"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-model-description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

One could insert a description of the background to their model here, to give
some context to what the model is trying to achieve. Remember that this vignette
is a technical document, so can go into some detail on specific methods used.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Methods

In the methods, the model should be explained. In particular how each of the 
units (functions) fit together to create the model. The individual help files generated
by `roxygen2` will provide information on each individual function but here
the reader should be guided through how the functins fit togher. 

This will likely result in more of a narrative, i.e. the model runs by running 
function **x** which returns a data frame fed into function **y**. It may justify the 
use of other packages and/or other languages/API calls (e.g. Python). It should outline 
where data is stored and how to retrieve it.

An example model run for a set of dummy inputs should be provided here, so that an 
interested party could run the model themselves.

```{r setup}
library(HECONpack)
```

# Results

Results can be shown here. These should include tables and plots. This way the 
reader knows what to expect when they run the model themselves. This is not the full 
modelling report so it doesn't have to read as such.

# Discussion

The description could include limitations, things that the modelling group would like
to improve in the future, and any strengths/weaknesses that a reviewer or third party
should be aware of. It may reference other related works.

# Conclusion

The conclusion should be brief. At this point a health economist who can program in R
should have everything they need to be able to replicate the analysis 
(albeit with dummy data) and review the model code.
